pirouette: Determining the error BEAST2 makes in inferring a phylogeny

### 2019-03-08 article.tex
Use generated LaTex table

  \textbf{1. }
    Epiitopiwef
    wefwe. \\
  \textbf{2. }
    ewfw
    ewfwf. \\
  \textbf{3. }
    ewfqef. \\
  \textbf{4. }
    wefwef. \\
\end{abstract}

{\bf Keywords:} computational biology, evolution, phylogenetics, BEAST2, pirouette, R

@@

@@

\begin{table}
\centering
  \begin{tabular}{| r | c | c | c | c | c | c |}
    \hline
    \textbf{Allele}       & \textbf{i} & \textbf{m} & \textbf{o} & \textbf{I} & \textbf{M} & \textbf{O} \\ 
    \hline
    DRB4*0101             & 3752 & 2397 & 62024 & 1061 & 854  & 11952 \\
    HLA-DPA10103-DPB10402 & 4335 & 2328 & 69040 & 478  & 923  & 4936 \\
    DQA1*0501/DQB1*0301   & 3321 & 1329 & 45461 & 1492 & 1922 & 28515 \\
    \hline 
  \end{tabular}
  \caption{
    \richel{These are preliminary, 6 percent of proteome}
    Location and binding of amino acids for the alleles.
    i: non-binding and inside, 
    m: non-binding and transmembrane, 
    o: non-binding and outside, 
    I: binding and inside, 
    M: binding and transmembrane, 
    O: binding and outside
  }
  \label{tab:results}
\end{table}

@@

Thanks to Geert van den Bogaart for his help.
We thank the Netherlands 
Organization for Scientific Research (NWO) for financial support 
through a VICI grant awarded to RSE.

>>>>

About a fourth of the human proteome is anchored by transmembrane helices (TMHs) to
lipid membranes. It, therefore, comes as no surprise that
bioinformatics analysis predicts an over-representation of TMHs among strong MHC
class I (MHC-I) binders. Published peptide elution studies confirm that TMHs are indeed
presented by MHC-I. This raises the question how membrane proteins are processed
for MHC-I (cross-)presentation, with current research focusing on soluble antigens. The
presentation of membrane-buried peptides is likely important in health and disease, as
TMHs are considerably conserved and their presentation might prevent escape muta-
tions by pathogens. Therefore, it could contribute to the disease correlations described
for many human leukocyte antigen haplotypes.

\end{abstract}

{\bf Keywords:} antigen presentation, antigen cross-presentation, membrane proteins, bioinformatics, adaptive
immunity, transmembrane domain, epitopes, T lymphocyte, MHC-2

@@

\cite{bianchi2017transmembrane}

@@

\begin{table}
\centering
  \begin{tabular}{| r | c | c | c | c | c | c |}
    \hline
    \textbf{Allele}       & \textbf{i} & \textbf{m} & \textbf{o} & \textbf{I} & \textbf{M} & \textbf{O} \\ 
    \hline
    DRB4*0101             & 3752 & 2397 & 62024 & 1061 & 854  & 11952 \\
    HLA-DPA10103-DPB10402 & 4335 & 2328 & 69040 & 478  & 923  & 4936 \\
    DQA1*0501/DQB1*0301   & 3321 & 1329 & 45461 & 1492 & 1922 & 28515 \\
    \hline 
  \end{tabular}
  \caption{
    \richel{These are preliminary, 6 percent of proteome}
    Location and binding of amino acids for the alleles.
    i: non-binding and inside, 
    m: non-binding and transmembrane, 
    o: non-binding and outside, 
    I: binding and inside, 
    M: binding and transmembrane, 
    O: binding and outside
  }
  \label{tab:results_old}
\end{table}

\input{table_imoimo.latex}
% has label tab:results

@@

Thanks to Geert van den Bogaart for his help \richel{reword}.
We thank the Netherlands 
Organization for Scientific Research (NWO) for financial support 
through a VICI grant awarded to RSE.
